Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2018-12-31 ongoing/report/article.tex
Complete basic literature survey

\newcounter{numResult}
\newcommand{\myCount}
{
   \stepcounter{numResult}
   \textbf{\arabic{numResult}}
}
%\newcommand{\qed}{\tag*{$\blacksquare$}}

@@

Multiple-input-multiple-output (MIMO) communication is adopted as the next generation of wireless communication scheme.
However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
It is then a non-trivial problem to estimate real-world wireless channels

Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing.
A promiment estimator is The Dantzig Selector proposed by Tao and Cand\'es.
In this article, we extend their proof to derive a specific bound in the setting of estimation of millimeter wave channel, utilizing an all-phase-shifter combiner in the receiver end.
Simulation compares our result and the

@@

@@

Millimeter waves communication has been proposed to be the next-generation specification.
The smaller wavelength entails higher frequency bands, and thus wider available bandwith to be available.
In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
Multiple-input multiple-output (MIMO) systems with a large number of antennae of both sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.

But MIMO presents new obstacles as well.
The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
It is important to devise feasible simulation method, as the systems themselves are growing more complicated, and the cost of simulations is large.

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(H\) at perfect CSI (here, the matrix form of \(H\)) is well-known, which is first proved by Teletar.
But that knowledge is hardly always available.
What makes things more difficult is the case that \(H\) is determined from not only \(n(\omega)\), but also parameter \(\theta\).
It is pointed out that the explicit form of \(C(\theta)\) is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Consequently, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.

In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
With more antennae present, conventional algorithms also increase in complexity and storage.
A design of new algorithms that addressed these issues is thus in need.

@@

Particularly relevant and inspiring to the present article is Cand\`es and Tao (2006), where they proposed a convex program called The Dantzig Selector (hencefore DS).
Cand\`es and Tao argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

Several notions related to compressed sensing are necessary in the presentation of results:

\myCount
\textbf{Definition}.
We call \(h \in \mathbb{R}^p\) to be \(S\)-sparse, for \(S =1,2,3,\dotsc\), if only \(S\) components of \(h\) is nonzero.

Denote as \(X_T\) the columns of \(X\) having indices in \(T\), where \(T \subset \{1,\dotsc,p\}\).

\myCount
\textbf{Definition}.
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|\theta\|^2
\leq \|X_T \theta\|_2^2
\leq (1+\delta_S) \|\theta\|^2
\end{gather}
RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).

It is shown that (Cand\'es and Tao 2005), in the noiseless case, the convex program
\begin{gather}
\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
\mathrm{subject}\; \mathrm{to} \quad X \hat{h} =y
\end{gather}
recovers \(\hat{h}\) completely if \(\delta_{S} +\delta_{2S} +\delta_{3S} <1\).

For concreteness, consider a channel with noise,
\begin{gather}
y =\sqrt{\mathcal{E}} X h +z
\end{gather}
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
(They also discussed specially the noiseless case, but we will not pursue the bounds here.)

How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
Let the following linear program, DS, be defined
\begin{gather}
\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
\mathrm{subject}\; \mathrm{to} \quad \|X^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -X \hat{h}\).

DS may be written as
\begin{gather}
\min_{x \in \mathbb{R}^p}  \|x\|_1 \\ \notag
\mathrm{subject}\; \mathrm{to} \quad \|Ax+b\|_\infty \leq c
\end{gather}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

The proof of DS is non-constructive, and it is not clear at first what matrices serves as the RIP condition.
But later, () have found there is a particularly convenient sufficient condition to verify RIP.
Tao explicitly remarked that the bound can be refined, but they did not undergo such task.

@@

Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
For example, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
They explore the estimation of single-antenna channel response with respect to time.
Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability.

@@

Then \(X\) is RIP of overwhelmingly probability.

The literature on CSS has since been vast, and we need not and cannot go through all of them here.
For example, Rao and Lau (2014) considers a rather complicated distributed algorithm where CSS is applied.
They consider a MU-MIMO problem that channels seen by various users share the same support, and proposes a modified joint OMP algorithm.
However, the sparsity of the channel is likewise merely made as an assumption.

Since the notice of hybrid beamforming, scholars have applied

J Lee, Gil, and Lee (2016), as an example, considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
Here, as usual, the beambook phase is quantized, and they have specifed a particular set of angles and argues the superiority.

Alkhateeb, Leus, and Heath Jr.\ poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.

They work simplified combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
However, their work mainly focuses on numerical simulation, rather than mathematical proof.

This being said, previous work only makes the assumption on the bound of the norm of the channel matrix, and, to the best knowledge of the author, has not characterized the such probability bounds as involving, say, number of channel paths and vector of array response.

@@

This article suggests a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.

Meanwhile, 
This serves partly as the foundation of performance analysis of 
An analysis of comparison of OMP with DS
Particularly worthy to note

But, in view of the requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than

Many papers have since cite Tropp and Gilbert (2007) only for justifying bound
But not always is a elementwise i.i.d.\ Gaussian.

After its advent, OMP becomes one of the most widely used channel estimation technique.
The sparsity of channel 
The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.

Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm.
Given a (beam) code book that corresponds to quantized AoA and AoD, they compare the power of (beam) code words in it, and choosing the column with 
Interestingly, their proof for probability bound of mistaken event does not base on Gilbert and Tropp (2007), but only involves the union bound and direct probabilistic integration.

Meanwhile Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
characterizes on MIP matrices.
Ben-Haim et.\ al.\ follow up their work and refine their bounds, also considering MIP conditions.
The \(\mu\) is easier to verify.
They serve as the guarantee for Alkhateeb et.\ al.\ (2015).

For example, Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ as the main foundation for OMP perfomance bound.
Ben-Haim et.\ al.\ conclude that OMP is better when

These works are very technical, and the author does not wish to dispute their accuracy.
Still, it remains unclear which of l1 and greedy is better.
The comparison on Ben-Haim splits the category of convex optimization and greedy.

The author argues that this article nevertheless considers a new configuration that, to the best of our knowledge, has not been dealt with.
First, we do not assume, like Lee et.\ al., that the virtual channel model is naturally quantized in its angle of departure and of arrival.
Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
The combiner made of relatively phase shifters serves readily as the sensing matrix that satisfy the RIP consideration.
Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
Our simple but typical model is expect to shed light on how CSS should be designed in face of phase quantizing and channel parameters available such as path numbers.

Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices.
in a modified basis pursuit problem.

Tropp and Gilbert put their techical proof on a standalone online document.
They restrict to i.i.d.\ Gaussian matrix.

@@

Before we start, let us remind that in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the title may be different from the source, but such case will be specified.

We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product.
Here the complex numbers has natural interpretation as the phasor of electronic waves.
Boldface lower case Latin alphabets denote vectors, and boldface upper case Latin alphabets denote matrices.

Denote \(\mathbb{E}\)
Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
Let the direct product
%
\begin{gather}
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
\end{gather}
%
denote the overall sample space, where:
%
\begin{itemize}
\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
\item \(\Omega_h\) denotes that of the communication channel,
\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
\item \(\Omega_r\) denotes that at the receiver end.
\end{itemize}
%
\(\omega_1\) stands for the probability index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

@@

\myCount
\textbf{Definition.}
Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).

\myCount
\textbf{Definition.}
For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
\myCount
\textbf{Lemma.}

@@

We recall that, as the author has argued above, existent literature often makes use of OMP, and exploit the relation

\begin{gather}
\mathrm{vec}(Y) -z
=\big[ (F_R^\dagger F_B^\dagger) \otimes (W_B W_R) \big] \mathrm{vec}(H)
\end{gather}

@@

\myCount
\textbf{Program}.
Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(Y\) is the acquired effective channel matrix under noisy observation.
Set the beamspace vector representation of \(H\) to be
\begin{gather}
\tilde{h} := \mathrm{vec}(H) \\
\tilde{y} := \mathrm{vec}(Y) \\
A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
\end{gather}
and set
\begin{gather}
r =\tilde{y} -A \tilde{h}
\end{gather}
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{\tilde{g}}
=\underset {{\tilde{h}}} {\mathrm{min}} \|\tilde{h}\|_1 \quad
\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{\tilde{g}}\) back to the space domain as
\begin{gather}
\hat{\tilde{h}}
=K^\dagger \hat{\tilde{g}}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\mathrm{vec}^{-1} (\hat{\tilde{h}}) \quad \blacksquare
\end{gather}

@@

\stepcounter{numResult}
\arabic{numResult}
\textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
And the function \(\mathbf{a}(\phi)\) is defined as in \eqref{}.
Then the discrete Fourier transform

@@

\stepcounter{numResult}
\arabic{numResult}
\textbf{Lemma}.
\begin{align}
\|\eta_Ah\|_2
\leq K_1 \|X^\dagger_{AB} X \eta\|_2 +K_2 \|\eta_C\|_2
\end{align}

@@

\stepcounter{numResult}
\arabic{numResult}
\textbf{Lemma}.
\begin{align}
\|\eta\|_2^2
\leq \|\eta_{AB}\|_2^2 +K_3 \|\eta_C\|_2^2
\end{align}

Another difference is that this article solves the optimization problem solely using the method of greatest descent.
While OMP is widely used 
With the analysis of [], OMP is usually used

@@

\subsection{Main Problem Written as an Convex Optimization Program}

\subsection{Primal-Dual Algorithm for Our DS Program}

Since our setting is slightly different
In this section we first describe the DS algorithm, which is our target of investigation, and briefly review the OMP algorithm, for sake of comparison.
As we see in the above, Dantzig Selector 
We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is well-known for convex optimization problems.

>>>>

\newcounter{NumResult}
\newcommand{\myCount}
{
   \stepcounter{NumResult}
   \textbf{\arabic{NumResult}}
}

\newcommand {\Result} [2]
{
   \bigskip
   \myCount \textbf{#1} \par
   {#2} \par
   \hfill \(\blacksquare\)
   \bigskip
}

@@

Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
It is then a non-trivial problem to estimate real-world wireless channels.

Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.

In this article, we utilize a hybrid structure at both transmitter and receiver end, consisting of both digital and analog percoders and combiners.
We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix

We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.

@@

This section is organized as follows.
Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
And we first provide the motivation, and then overview the existent literature on channel estimation.
Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.

Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.

We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.

Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).

@@

Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
But MIMO presents new obstacles as well.
The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
Consequently, this article considers MIMO in the millimeter r\`egime.

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
But that knowledge is hardly always available.
What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).

Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithm also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus in need.

\subsection{Recovery of Sparse Vector in the Noiseless Case}

They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.

\Result
{Definition}
{
\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \{\mathrm{supp}(x)\} \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
\mathrm{s.t.} \quad Ax =y
\end{gather}
}

\Result
{Theorem}
{
Let \(y =Ax\).
Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
\begin{gather}
\delta_{S} +\delta_{2S} +\delta_{3S} <1
\end{gather}
}

\Result
{Notation}
{
Let \(T \subset \mathbb{N}\).
Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
}

\Result
{Definition}.
{
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|\theta\|^2
\leq \|X_T \theta\|_2^2
\leq (1+\delta_S) \|\theta\|^2
\end{gather}
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).

@@

Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

For concreteness, consider a liear transformation with noise,
\begin{gather}
y =Ax +z
\end{gather}
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

\subsection{Condition of RIP Linear Transformation}

The constant \(\delta\) in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.

Here, it is not clear at first what matrices serves as the RIP condition.
But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
\begin{gather}
   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp(-n c_0(\epsilon))
\end{gather}
where we have
\begin{gather}
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
\end{gather}
}

@@

We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
Some scholars thus has applied compressive sensing techniques to the problem.

One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.

@@

Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.

\subsection{Orthogonal Matching Pursuit}

Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

\Result
{Algorithm}
{
\begin{enumerate}
\item
\end{enumerate}
}

\Result
{Theorem}
{
   Following the setting described above, suppose, for \(0 <\delta <1\),
\begin{gather}
   M \geq 16s \log (N/\delta)
\end{gather}
Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
}

For the proof, see the technical report: Tropp and A C Gilbert (2007a).

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
\begin{gather}
y =WHF x
\end{gather}

\Result
{Definition}
{
Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
}

\Result
{Definition.}
{
For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
}

With (), scholars often exploit the relation
\begin{gather}
\mathrm{vec}(Y)
=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
\end{gather}

The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.

\subsection{Further development on CSS}

The literature on CSS has since been vast, and we need not and cannot go through all of them here.
Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.

Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.

Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.

Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
Their work mainly focuses on numerical simulation, rather than mathematical proof.

Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).

Meanwhile, the improvement of OMP bound is also going on.
Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.

Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.

Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.

Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.

@@

We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.

\begin{enumerate}
\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
\end{enumerate}

We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.

Our contribution include:

\begin{enumerate}
\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
\end{enumerate}

@@

Let the direct product
%
\begin{gather}
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
\end{gather}
%
denote the overall sample space, where:
%
\begin{itemize}
\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
\item \(\Omega_h\) denotes that of the communication channel,
\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
\item \(\Omega_r\) denotes that at the receiver end.
\end{itemize}
%
\(\omega_1\) stands for the probability index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

@@

@@

@@

\myCount
\textbf{Program}.
Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(Y\) is the acquired effective channel matrix under noisy observation.
Set the beamspace vector representation of \(H\) to be
\begin{gather}
h := \mathrm{vec}(H) \\
\tilde{y} := \mathrm{vec}(Y) \\
A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
\end{gather}
and set
\begin{gather}
r =\tilde{y} -A h
\end{gather}
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{\tilde{g}}
=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{\tilde{g}}\) back to the space domain as
\begin{gather}
\hat{h}
=K^\dagger \hat{\tilde{g}}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\mathrm{vec}^{-1} (\hat{h})
\end{gather}

@@

\myCount
\textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
And the function \(\mathbf{a}(\phi)\) is defined as in \eqref{}.
Then the discrete Fourier transform

@@

\Result
{Lemma}
{
\begin{align}
\|\eta_Ah\|_2
\leq K_1 \|X^\dagger_{AB} X \eta\|_2 +K_2 \|\eta_C\|_2
\end{align}
}

@@

\Result
{Lemma}
{
\begin{align}
\|\eta\|_2^2
\leq \|\eta_{AB}\|_2^2 +K_3 \|\eta_C\|_2^2
\end{align}
}

@@

As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.

\subsection{Transformation into Second Order Cone Problem}

Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
Recapitulate that, as we explained in the above, DS involves a 
We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
